Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-11 Ben_Manuscripts/structure_paper/Draft.tex
Edits and figure updates

\documentclass[journal=jpcbfk,manusciprt=article]{achemso}

@@

  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
  average distance between stacked monomers, and an amplitude that decays exponentially
  (See Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
  to a decaying exponential function of the form:
  \begin{equation}
  	Ae^{-z/L}
  \end{equation}
  where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
  and L is the fit correlation length. The error in the estimated value of L is 
  calculated as the square root of the diagonal entry of the covariance matrix of 
  optimized fit parameters.

@@

  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
  spacing, \textit{d}, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
  monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
  of the supporting info for more details on sensitivity to initial layer spacing). 
  The pore-to-pore spacing is equilibrated, as defined in section~\ref{method:equil_time},
  % BJC5: this achemso format does not have section numbers so I can't reference sections
  % within this document.
  in all systems after 400 ns of simulation. Figure~\ref{fig:p2p} shows the equilibrated
  pore-to-pore distances for all systems tested.

  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
  systems built with 5 columns per pore. Systems built with 6 columns per pore, and 
  $\mathit{d}=3.7~\AA~$, have an equilibrated pore spacing c.a. 0.50 nm higher than experiment.
  Systems built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower
  than experiment.

  %BJC5: thesis needs rewording.
  Systems built with 6 columns-per-pore and $\mathit{d}=5~\AA~$ are not compact
  in the z-direction. The final pore spacing is close to experiment within its uncertainty.
  Relative to 6 column-per-pore systems started with $\textit{d}=3.7~\AA~$, the unit cell
  is elongated in its z dimension and contracted in its x and y dimensions, however the
  box volume stays nearly constant in all cases (Figure~\ref{fig:box_dimensions}). The system
  is likely not fully equilibrated and may eventually rearrange into something that resembles
  a 5 column-per-pore system. Further investigations into this are beyond the scope of this
  paper.

@@

  All systems tested are at least metastable on the timescales studied here, however not all 
  make physical sense or fit the experimental profile that we are trying to match. In the limit
  of infinite simulation time, all simulations will converge to a single density. It is our 
  intention to choose an initial configuration which quickly reaches a monomer density close 
  to experiment. We believe systems built with 5 columns per pore achieve this goal.

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K with monomers initially stacked
  3.7 \AA~and 5.0 \AA~apart. We generated simulated patterns using portions
  of simulation trajectory after equilibration. The patterns for all structures are
  shown and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

			\begin{subfigure}{\textwidth}
			\centering
		    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			        %\caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
	experiment. Shown is a comparison of the (a) Sandwiched, d=3.7~\AA~ (b) Sandwiched,
	d=5~\AA~(d) Parallel Displaced, d=3.7~\AA~ and (e) Parallel Displaced, d=5~\AA~ 
	configurations with (c) experimental WAXS. Quantitative comparisons of the relative 
	intensities of reflections of interest are present in Table~\ref{table:relative_inensities_300K}. 
	In all cases, R-double is not present.}~\label{fig:XRDsim} 
  \end{figure}

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
  the wide R-$\pi$ reflection. R-$\pi$ appears at a lower $q_z$ value than experiment. In all
  systems, the reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers 
  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. This behavior is not surprising 
  since GAFF models atoms as point charges and does not appropriately model the aromatic
  $\pi-\pi$ interactions which would cause the monomers to stack closer together. R-double 
  does not appear in any of the patterns.

@@

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. There are horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not appear for the same reason as R-double. This type of pattern
  is characteristic of a helix (reference something).
  %BJC5: reference something like a dna diffraction paper
  It is possible that these reflections contribute to the continuation of R-double into R-
  alkanes, as seen in the experimental pattern.
  %BJC5: not sure above sentence is clear (or necessary to say)

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

@@

  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
  is most intense in the sandwiched configuration (Figure~\ref{fig:sandwiched280K}). The relative 
  intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still not present.  
  We will use this configuration to more thoroughly explore the origin of R-spots.

@@

  The R-spots signal is not a result of alkane chain tilt. Previous literature
  has attributed the spots in this particular WAXS pattern as the product of tilted alkane
  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
  configuration simulated at 280K. We measured the tilt angle of the alkane chains and 
  showed that our system equilibrates to an average tilt angle close to zero degrees
  (Fig.~\ref{fig:tilt}).

   %BJC5: bootstrap this data to make it smoother.
  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

@@

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
  location where the highest intensity of spots are located on the simulated
  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
  performed the same integration on the raw experimental data and found the angle
  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
  is a reconcilable difference with our simulated results.

@@

  There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
  experimental conditions of 300 K.
  \begin{enumerate}
  		\item The difference between 280K and 300K is small. Our forcefield parameters
  		may not correctly model the behavior of the tails at 300K (citation?).
  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
  		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
  		to pack between vertically adjacent monomer tails. In our case, the tail region is
  		less dense than experiment which gives the tails freedom to organize in a more
  		entropically favored disordered state. 
  \end{enumerate}

@@

  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}).

  %BJC5: redo after discussing with Michael
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
  \caption{}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.png}
  \caption{}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  %BJC4: This is noisier than l=3.7 angstrom, but I can still pick out peaks. I'm unsure
  % how to quantify the difference. The correlation length is very similar to the more
  % ordered configuration.
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
  \caption{}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  %BJC4: There really aren't any good peaks here. 
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
  \caption{}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{}\label{fig:correlation}
  \end{figure}

  %BJC5: conclusions here will need modification
  The correlation length between stacked monomer head groups shows the best agreement with
  experimental for systems simulated in the ordered basin.
  %BJC4: explanation of correlation function calculation in methods section. 
  %MRS5: the correlation length doesn't look like that great a fit, since it misses the first point by so much.  We may need to reevaluate a litle how this is done. 
  %BJC5: forgot an amplitude on exponential fit. New results show lower correlation length
  We calculated correlation length by fitting a decaying exponential function to all peaks of
  $g(z)$ for the sandwiched configuration and to every other peak of $g(z)$ for the parallel
  displaced configuration. The correlation length of systems simulated in the ordered basin are
  11.2 \AA and 14.9 \AA	for the parallel displaced and sandwiched configurations respectively. 
  %BJC5: Something about disordered systems.
  Systems simulated in the ordered basin show correlation closest to the experimental correlation
  length of 10.1 \AA. They are still slightly more correlated than experiment which would lead to
  an increase in constructive X-ray scattering. 
  %BJC5: this statement might not be true anymore.

  Additionally, our system models near-perfectly straight pores with no defects which will
  lead to higher intensity vertical stacking reflections. Nearly all of the intensity in R-$\pi$
  of our simulated patterns is concentrated at a single point. Figure ~\ref{fig:intense_rpi}
  shows the same simulated patterns with the upper boundary on the colorbar adjusted to be 6x
  higher. The only distinguishable reflections are those of R-$\pi$ and R-pores. In the 
  experimental pattern, the intensity is more evenly spread out over all of R-$\pi$.

  \begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{sandwich_rzplot_highlimit_cbar.png}
  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections. Here, the 
  colorbar was scaled so that the max is 6x higher than all other plots.}\label{fig:intense_rpi}
  % BJC5: could benefit from an adjusted colorbar experimental pattern.
  \end{figure}

@@

%  with neighboring layers up to more than 10 layers away. This behavior deviates

@@

  We can produce R-double if our initial configuration contains alternating parallel and
  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). It is difficult to physically
  justify this system. Systems built this way are only stable if position restraints are placed
  on all head group heavy atoms. Carboxylate groups quickly revert to the parallel position as 
  restraints are released. There is an appreciable energy barrier that prevents rotation
  of carboxylate groups attached to phenyl rings since the group extends the system's 
  $\pi$ conjugation. (citation) (See figure in supporting info with energy barrier plots)
  %BJC5: add citation for extended pi conjugation
  %BJC5: add figure reference and figure to supporting info
  There are instances where carboxylate groups in other systems rotate out of plane. Bushey et
  al. showed that bulky carbonyl-containing substituents of stacked arene molecules tended to
  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-stacking between 
  molecules, and to hydrogen bond with neighboring molecules. Lorenzo and Gra\~{n}a found 3
  stable dimers of gallic acid (from which the monomer, Na-GA3C11 is derived) with adenine. In
  all cases, the carboxylate group remained planar, even with evidence of hydrogen bonding
  between the carboxyl group and nitrogen atoms of adenine. The monomers which we are studying
  have no opportunities to hydrogen bond and are confined so that any rotation about the phenyl--
  carboxylate bond would be sterically hindered.

>>>>

\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
%\documentclass{article}
%jpcbfk

@@

  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
  average distance between stacked monomers, and an amplitude that decays exponentially
  (See Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
  to a decaying exponential function of the form:
  \begin{equation}
  	Ae^{-z/L}
  	\label{eqn:decaying_exponential}
  \end{equation}
  where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
  and L is the fit correlation length. The error in the estimated value of L is 
  calculated as the square root of the diagonal entry of the covariance matrix of 
  optimized fit parameters.

  We also used $g(z)$ to calculate the equilibrated vertical stacking distance between
  monomers, $\mathit{d}_equil$. 
  %BJC5: in case there is an criticism of this method
  %The simplest way to do so, would be to fourier transform
  %$g(z)$ and extract the highest amplitude frequency of the resulting fourier series. 
  %However, the size of our system limits the width of the bins in fourier space. The bins
  %are too large to extract a precise value of $\mathit{d}_equil$. Instead, 
  We fit a decaying sinusoidal function to $g(z)$ of the form:
  \begin{equation}
  	1 - Acos(\frac{2\pi}{\mathit{d}_{equil}}z + B)e^{-z/L}
  	\label{eqn:decaying_sinusoid}
  \end{equation}
  where A and B are fit parameters for the function's amplitude and phase shift respectively.
  This function could be used in place of Equation~\ref{eqn:decaying_exponential}, however
  it does not fit the peaks of $g(z)$ from parallel displaced configurations well enough
  to extract a reliable value of L.
  %BJC5: maybe include plots of these fits in supporting info

@@

  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
  monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
  of the supporting info for more details on sensitivity to initial layer spacing). 
  The pore-to-pore spacing was considered equilibrated, as defined in section~\ref{method:equil_time},
  % BJC5: this achemso format does not have section numbers so I can't reference sections
  % within this document.
  in all systems after 400 ns of simulation. Figure~\ref{fig:p2p} shows the equilibrated
  pore-to-pore distances for all systems tested.

  All systems tested, although equilibrated from the perspective of the metrics used here, are
  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
  we are trying to match. In the limit of infinite simulation time, all systems will converge to
  a single equilibrium configuration. For simplicity, we will group the systems studied here into
  the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
  ordered basin and any system where $\mathit{d}=5.0$ \AA will be included in the disordered basin.
  The reason for these names will become clearer as we progress through our analysis.

%    All systems tested are at least metastable on the timescales studied here, however not all 
%  make physical sense or fit the experimental profile that we are trying to match. In the limit
%  of infinite simulation time, all simulations will converge to a single density. It is our 
%  intention to choose an initial configuration which quickly reaches a monomer density close 
%  to experiment. We believe systems built with 5 columns per pore achieve this goal.

  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
  systems built with 5 columns per pore. Ordered basin systems built with 6 columns per pore,
  have an equilibrated pore spacing c.a. 0.50 nm higher than experiment. Ordered basin systems
  built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower than experiment.

  %BJC5: thesis needs rewording.
  Disordered basin systems built with 6 columns-per-pore are not compact in the z-direction.
  The final pore spacing is close to experiment within its uncertainty. Relative to ordered basin 
  6 column-per-pore systems, the unit cell is elongated in its z dimension and contracted in its
  x and y dimensions, however the box volume stays nearly constant in all cases 
  (Figure~\ref{fig:box_dimensions}). The system is likely not fully equilibrated and may eventually
  rearrange into something that resembles a 5 column-per-pore system. Further investigations 
  into this are beyond the scope of this paper.

@@

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. We tested systems built with 5 columns per pore in the parallel 
  displaced and sandwiched configurations at 300 K in the ordered and disordered
  basins. We generated simulated patterns using portions of simulation trajectory after
  equilibration. The patterns for all structures are shown and compared to experiment
  in Figure~\ref{fig:XRDsim}.

@@

			\begin{subfigure}{\textwidth}
			\centering
		    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			        %\caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
	experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
	disordered basin (d) Parallel Displaced, ordered basin and (e) Parallel Displaced, disordered basin 
	configurations with (c) experimental WAXS. Quantitative comparisons of the relative 
	intensities of reflections of interest are present in Table~\ref{table:relative_inensities_300K}. 
	In all cases, R-double is not present.}~\label{fig:XRDsim} 
  \end{figure}

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
  the wide R-$\pi$ reflection. R-$\pi$ appears at a lower $q_z$ value than experiment. In all
  systems, the reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers 
  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. R-double does not appear in any
  of the patterns.

@@

  The simulated XRD patterns of the parallel displaced configurations show an additional
  reflection due to their helical structure. There are horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not appear for the same reason as R-double. This type of pattern
  is characteristic of a helix (reference something).
  %BJC5: reference something like a dna diffraction paper
  It is possible that these reflections contribute to the continuation of R-double into R-
  alkanes, as seen in the experimental pattern.
  %BJC5: not sure above sentence is clear (or necessary to say)

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

  %BJC5: I think something like this has to go somewhere.
  The diffraction patterns show some noise, especially along the $q_z$ axis where $q_r$=0. This
  noise can be suppressed by sampling more uncorrelated equilibrium configurations. Unfortunately,
  our simulations are not long enough to sample enough independent configurations. Increasing the
  number of trajectory frames used to simulate the structure factor within a given interval of time
  does not offer any improvement.
  %BJC5: maybe show in supplemental?

@@

  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
  The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still
  not present. We will use this configuration to more thoroughly explore the origin of R-spots.

@@

  The R-spots signal is not a result of alkane chain tilt. Previous literature
  has attributed the spots in this particular WAXS pattern as the product of tilted alkane
  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched configuration simulated
  at 280K. We measured the tilt angle of the alkane chains and showed that our system 
  equilibrates to an average tilt angle of -2\degree (Fig.~\ref{fig:tilt}).

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

@@

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails}
  are located at $\pm 33 \degree$ which is the same location where the highest
  intensity of spots are located on the simulated patterns. We confirmed this 
  conclusion by radially integrating the 2D WAXS pattern for 
  $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe distinct peaks ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figure~\ref{fig:layered_integration}). We performed the same integration on
  the raw experimental data and found the angle at which R-spots reaches its
  highest intensity to be $\pm 37 \degree$ which is a reconcilable difference
  with our simulated results.

@@

  There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
  experimental conditions of 300 K.
  \begin{enumerate}
  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
  		may not correctly model the behavior of the tails at 300 K (citation?).
  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
  		to pack between vertically adjacent monomer tails. In our case, the tail region is
  		less dense than experiment which gives the tails freedom to organize in a more
  		entropically favored disordered state. 
  \end{enumerate}

@@

  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). We used this 
  information to understand how far apart monomers stack within monomer columns and
  the degree to which they are correlated.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.png}
  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{1D correlation functions of the center of masses of aromatic head groups, $g(z)$, show
  decaying oscillatory behavior. We calculated the correlation length by fitting a decaying exponential
  function (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The correlation length is
  longer for ordered basin systems (Table~\ref{table:correlation_length}).
  We did not attempt to calculate the correlation length for (d) because there are no clear peaks. We 
  assume that its correlation is less than the vertical distance between monomers.}\label{fig:correlation}
  \end{figure}

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
  \midrule
  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.5 $\pm$ 0.4            \\
  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 15.5 $\pm$ 1.9           \\ 
  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $\mathit{d}_{equil}$ \\ 
  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
  \bottomrule
  \end{tabular}
  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
  \label{table:correlation_length}
  \end{table}

  Monomers in the ordered basin stack closer together than those in the disordered basin
  (Table~\ref{table:correlation_length}). We calculated the equilibrated vertical distance,
  $\mathit{d}_{equil}$, between monomers using Equation~\ref{eqn:decaying_sinusoid}. 
  Monomers in the ordered basin stack ca. 0.2 and 0.3 \AA~closer than those built in the 
  disordered basin in the sandwiched and parallel displaced configurations respectively. 
  The distance between stacked monomers is greater than experiment by 0.5 - 0.9 \AA~across all 
  cases. This behavior is not surprising since GAFF models atoms as point charges and does not 
  appropriately model the aromatic $\pi-\pi$ interactions which would cause the monomers to 
  stack closer together. Ordered basin systems are likely the best choice for transport studies.

  The correlation length between stacked monomer head groups of the ordered systems also show
  closer agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
  not extract a reliable correlation length from the disordered parallel displaced configuration.
  The amount of noise in the correlation function and the lack of an initial peak suggests that 
  the correlation length is less than $\mathit{d}_{equil}$. In general, we see that correlation
  length increases as monomers stack closer together. The same trend has been seen in molecular
  dynamics studies of polymer fluids~\cite{koshy_density_2003}. We hypothesize that the correlation
  length of the sandwiched configuration would increase to a value near experiment if monomers
  packed closer together.

  The persistent oscillatory behavior of the correlation function may in part explain the high
  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
  simulated systems, especially the sandwiched configurations, shows peaks which persist across
  the entire correlation function. If the peaks at large values of z instead decay to 1 uniformly,
  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
  The monomer head groups in our simulations do not move enough to create the noise which would 
  cause such behavior. See Section TBD of the supporting information for illustrative examples. 
  % BJC5: Trying using inverted fourier transform of 2D experimental waxs. See what z-cross-section
  % looks like (does it oscillate more or less?) Then take FT of that and compare its intensity
  % to simulated intensity

  The simulated intensity of R-$\pi$ is also more intense than experiment because our system
  models near-perfectly straight pores with no defects. Nearly all of the intensity in 
  R-$\pi$ of our simulated patterns is concentrated at a single point. Figure~\ref{fig:simulated_adjusted_colorbar}
  shows the simulated pattern of the ordered sandwiched configuration with the upper boundary
  on the colorbar adjusted to be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only
  distinguishable reflections are those of R-$\pi$ and R-pores. In the experimental pattern 
  (Figure~\ref{fig:experimental_adjusted_colorbar}, the intensity is more evenly spread out
  over all of R-$\pi$. 
  % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
  % out what to do about it
  % BJC5: Could it also be related to noise in xy direction?
  % BJC5 : I think my original intent was to explain it as tortuosity. But it's not clear if the
  % reflection is arced

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
	  \caption{}\label{fig:simulated_adjusted_colorbar}
  \end{subfigure}
  \begin{subfigure}{0.4\textwidth}
	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
	  \caption{}\label{fig:experimental_adjusted_colorbar}
  \end{subfigure}
  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
  simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
  higher than all other plots.}\label{fig:intense_rpi}
  \end{figure}

@@

%  with neighboring layers up to more than 10 layers away. This behavior deviatbecomes smalleres

@@

  We can produce R-double if our initial configuration contains alternating parallel and
  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). It is difficult to physically
  justify this system. Systems built this way are only stable if position restraints are placed
  on all head group heavy atoms. Carboxylate groups quickly revert to the parallel position as 
  restraints are released. There is an appreciable energy barrier that prevents rotation
  of carboxylate groups attached to phenyl rings since the group extends the system's 
  $\pi$ conjugation. (citation) (See figure in supporting info with energy barrier plots)
  %BJC5: add citation for extended pi conjugation
  %BJC5: add figure reference and figure to supporting info
  There are instances where carboxylate groups in other systems rotate out of plane. Bushey et
  al. showed that bulky carbonyl-containing substituents of stacked arene molecules tended to
  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-$\pi$ stacking between 
  molecules, and to hydrogen bond with neighboring molecules. Lorenzo and Gra\~{n}a found 3
  stable dimers of gallic acid (from which the monomer, Na-GA3C11 is derived) with adenine. In
  all cases, the carboxylate group remained planar, even with evidence of hydrogen bonding
  between the carboxyl group and nitrogen atoms of adenine. The monomers which we are studying
  have no opportunities to hydrogen bond and are confined so that any rotation about the phenyl--
  carboxylate bond would be sterically hindered.
